MP MetaAnalysis

### 2018-11-24 Paper_Analyses.Rmd
small updates to manuscript, towards a final exploratory analysis

affiliation:
  - id            : "1"
    institution   : "Language Development Laboratory, University of Maryland, USA"
  - id            : "2"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "3"
    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
  - id            : "4"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

@@

@@

# moderator test
mod_test <- function(x) paste0("QM(", r2(rma_MPeffect$m), ") = ", r2(rma_MPeffect$QM), ", *p*", psig(rma_MPeffect$QMp))

@@

Acquiring a first language means that young learners are solving a host of tasks in a short amount of time. As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [Primir, Kuhl, Best]. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g. cat-hat). To build robust language knowledge, it seems ueful to acquire this ability early during development. Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning []. This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words. As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what consistutes a permissible versus word-changing phonological deviation. In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.

  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded and subsequently coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. "baby"). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. "vaby"). The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it\s the right term]

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary mechanisms in early phonological development: *phonological constancy* and *phonological distinctiveness*, which are both present in the mature language processing system. Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat. To successfully recognize words, speakers of a given language must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning. Both abilities have to be acquired, because language systems differ in which sounds signal a meaning change.

  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year. There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

@@

  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative. One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features). 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed. 24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations. In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.

@@

```{r SummaryTable}

@@

```
[Christina] I've shortened the labels and wanted to try out apa_table

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We screened the resulting 398 items, removing 99 duplicate items. We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

@@

comparison_info <- db_ET_correct %>%
  group_by(within_measure_descriptive) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

@@

```
[Christina] I think it would be useful to say how many records, not papers, report each measure. e.g. "(n = xxx records from yyy papers)". Would that be ok?

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper. Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.

[Christina] Katie, do you know whether the difference is computed based on items, participants, trials...? Is there consistency?

Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`). For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e. a recognition effect. Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

[Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, n_distinct(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(es_info, n_distinct(n_unique[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all significant effect being spurious. 
Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior, with some studies reporting no significant looks to the target when hearing a mispronounced label

[Christina] Katie, is that right, can you add a citation?

@@

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error. We therefore continue with our moderator analysis to investigate possible sources of this variance.

[Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?

@@

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). 
[Christina] What about the whole months thing?

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounce words (`r mod_test(rma_MP_age)`). The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

[Christina] OK there is a mismatch between what you write and the numbers, can you verify?

@@

```{r VocabularyData, echo = FALSE}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n(),
            papers = n_distinct(short_cite))

@@

vocab_info2 <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
                            "none")) %>%
  group_by(has_vocab) %>%
  summarize(count = n(),
            papers = n_distinct(short_cite))

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`). There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.

[Christina] Removed the previous comment chaos.
So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this? Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab. 
Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.

```{r ComprehensionMeta_correct}
#we're relying on the library meta function metacor
compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)

@@

@@

```{r ProductionMeta_correct}
#we're relying on the library meta function metacor
prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)

CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")

@@

[Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]
[Christina] looks good to me.

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48. The mean effect size XXX was small with 0.0897, which did not differ significantly from zero (CI [-0.0105; 0.1900] *p* = .0795). However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant. At the same time, a larger sample might confirm our conclusion that there is no relationship.

Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44. The mean effect size XXX was again small and not significantly different from zero with 0.0601 (CI [-0.0331; 0.1533] *p* = .2061). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations. However, we note again that comparatively few studies report the correlation between vocabulary and infants' responses to correct pronunciations to begin with and thus we cannot draw any firm conclusions based on this small sample of studies.

[Christina] I think bc the effect is small but apparently consistent, we can reason that we might have a power problem and thus cannot draw firm conclusions.

@@

MC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

```{r ProductionMeta_MP}
#we're relying on the library meta function metacor
prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)

MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

>>>>

affiliation:
  - id            : "1"
    institution   : "Department of Hearing and Speech Sciences, University of Maryland, USA"
  - id            : "2"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "3"
    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
  - id            : "4"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

@@

# can't call reshape here, because it will interfere with other libraries
#library(reshape)

@@

# moderator test
mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p*", psig(x$QMp))

@@

Acquiring a first language means that young learners are solving a host of tasks in a short amount of time. As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [Primir, Kuhl, Best]. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g. cat-hat). To build robust language knowledge, it seems ueful to acquire this ability early during development. Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [Clark & Clark, 1977]. This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words. As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what consistutes a permissible versus word-changing phonological deviation. In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.

  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded and subsequently coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. "baby"). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. "vaby"). The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *object identification*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it's the right term]
[Katie: Karen (Mulak) talks about these terms as concepts. Mechanisms to me means some sort of internalization, that they would have had this ability all along and just need to apply it. It could be that we fundamentally disagree on this, but to me these are things that infants discover. Later on we use principles. What about "principles that infants must discover"... "in order to form adult-like word representations"? I took away "which are both present in the mature language processing system".]

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary principles that infants must discover in early phonological development in order to form adult-like word representations: *phonological constancy* and *phonological distinctiveness*. Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat. To successfully recognize words, speakers of a given language must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning. Both abilities have to be acquired, because language systems differ in which sounds signal a meaning change.

[Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]

  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year. There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively supported by single studies and two predicted by theoretical accounts. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

@@

  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 9 months (Bergelson & Swingley, 2017), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative. One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features). 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed. 24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations. In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.

@@

```{r SummaryTable, results = "asis"}

@@

```
[Christina] I've shortened the labels and wanted to try out apa_table
[Katie] I like the idea, but does it work for you? It doesn't work for me...
[Katie] We have it currently set at less than 31 months, not 36, so I've changed below.

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We screened the resulting 398 items, removing 99 duplicate items. We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

@@

comparison_info <- db_ET_correct %>%
  group_by(within_measure) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

@@

```
[Christina] I think it would be useful to say how many records, not papers, report each measure. e.g. "(n = xxx records from yyy papers)". Would that be ok?
[Katie] Totally! I think that gives a good bit of information. Good suggestion!

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper. Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.

[Christina] Katie, do you know whether the difference is computed based on items, participants, trials...? Is there consistency?
[Katie] From working with Nivi, we did it participants x condition or participants x trial (but mostly the former). But, this is not something we reported in papers. I don't think I read it at all when putting together the dataset for this either.

Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers). For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e. a recognition effect. Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

[Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?
[Katie] Well, they are kind of wrong :) Two papers report both for different experimental conditions. I've given the explanation now, not sure if that is good enough, but I'm really not sure how to say it a different way.
[Katie] Do you want number of records and papers for the imputed correlations as well? You've put a -1, assuming there was something wrong with one of the papers or something like that? How does that shake out for number of records?

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers). Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all significant effect being spurious. 
Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior. In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but some studies may report either significant looks or no  significant looks to the target when hearing a mispronounced label

[Christina] Katie, is that right, can you add a citation? 
[Katie] I've rewritten it a bit to be explicit about the difference between expectations for correct and mispronounced labels. I'm not sure what to cite though. The papers that find significant looks or no significant looks? That's basically the meta-analysis. Or some citation that talks about what looking to the target upon hearing a mispronunciation means in comparison to what target looks being decreased for mispronunciations relative to correct pronunciations means? I'm not so sure whether anyone has actually talked about that difference before, not sure what to cite.

@@

[Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?
[Katie] I think that makes sense, moving it!

@@

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`), as well as mispronunciation sensitivity, which included the moderator condition, (QE(249) = `r r2(rma_MPeffect$QE)`, *p* `r psig(rma_MPeffect$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error. We therefore continue with our moderator analysis to investigate possible sources of this variance.

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 2). 
[Christina] What about the whole months thing?
[Katie] We had an explanation in the methods section for this, I've now added it again here.

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`). The lack of a significant modulation together with the small estimates (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. We plot both object recognition and mispronunciation sensitivity as a function of age in Figure 2.

[Christina] OK there is a mismatch between what you write and the numbers, can you verify?
[Katie] Good catch. For some reason, it was just copying over the moderator test from mispronunciation sensitivity, even though I was calling for the age moderator analysis. There is no significant moderator test, but it was just pasting the same one again and again. I've fixed my code, so it should be correct now!

@@

```{r VocabularyData, echo = FALSE}
vocab_info <- dat %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n(),
            papers = n_distinct(short_cite))

@@

vocab_info2 <- dat %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
                            "none")) %>%
  group_by(has_vocab) %>%
  summarize(count = n(),
            papers = n_distinct(short_cite))

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records). There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Kidd citation), and we therefore planned to analyze these two types of vocabulary measurement separately. However, only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, limiting the conclusions that can be drawn. In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.

[Christina] Removed the previous comment chaos.
So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this? Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab. 
Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.
[Katie] I couldn't find what you are referring to. Could you add the Evan Kidd paper? Also, I added a histogram figure below, but I'm not so very sure that it is good enough to add to the paper (its under the heading "Potential Vocabulary Figure"). Let me know what you think.

```{r ComprehensionMeta_correct}

# coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results

#we're relying on the library meta function metacor
compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)

@@

# number of positive correlations
#CC$TE
rel <- ifelse(CC$TE > 0, "pos", "neg")
pos_rel <- sum(rel == "pos")
neg_rel <- sum(rel == "neg")
tot_rel <- pos_rel + neg_rel

min_cor <- min(CC$TE)
max_cor <- max(CC$TE)

@@

```{r ProductionMeta_correct}
#we're relying on the library meta function metacor
#prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)

#CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")

#Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44. The mean effect size XXX was again small and not significantly different from zero with 0.0601 (CI [-0.0331; 0.1533] *p* = .2061). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations. However, we note again that comparatively few studies report the correlation between vocabulary and infants' responses to correct pronunciations to begin with and thus we cannot draw any firm conclusions based on this small sample of studies.

@@

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`. The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`). However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant. At the same time, a larger sample might confirm our conclusion that there is no relationship. As a result, we can not draw firm conclusions about the relationship between comprehension scores and object recognition in response to correct pronunciations.

@@

MC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")

# number of positive correlations
#CC$TE
rel <- ifelse(MC$TE > 0, "pos", "neg")
pos_rel <- sum(rel == "pos")
neg_rel <- sum(rel == "neg")
tot_rel <- pos_rel + neg_rel

min_cor <- min(MC$TE)
max_cor <- max(MC$TE)

```{r ProductionMeta_MP}
#we're relying on the library meta function metacor
# prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
# 
# MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")

#For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402, (CI [-0.1043; 0.0238] *p* = .2181).
